On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-07 main.tex
Minor S4 updates

To estimate the degree of $\D_{i}$, what remains is to give an upper
bound on the degree of $\alpha_i,\dots,\alpha_n$. This will come as an
application of the effective Nullstellensatz given in~\cite{EN}, for
which we first need to determine degree bounds, separately in $\Xb,T$
and $\A,$ of the polynomials in the membership relationship. We have
\begin{align*}
\deg_{\Xb,T}\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\}&\leq d\\
\deg_{\A}  
\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\}& \leq d\\
\deg_{\Xb,T}(1-T\pjb) &\leq (2d)^n +1 \\
\deg_{\A}(1-T\pjb)& \leq (2d)^n.
\end{align*}
For each $j \in \{i,\hdots,n\},$ a direct application of \cite[Theorem
0.5]{EN}, gives $\deg(\alpha_j) \le (n+1)d^n((2d)^n+1)$; we will use
the slightly less precise bound $\deg(\alpha_j) \le 2n(2d)^{2n}$.

We saw in Section~\ref{ssec:Hi1} that $\D_{i,1}$ has degree at most
$2nd^{2n}$, and all $D_j$'s have degree at most $(2d)^n$. This gives
the upper bound
$$\deg(\D_i) \le 2nd^{2n} + 2n^2(2d)^{2n} + n(2d)^n \le 6n^2 (2d)^{2n}.$$
This finishes the proof of Theorem~\ref{theo:gen}.

>>>>

To estimate the degree of $\D_{i}$, what remains is to give an upper
bound on the degree of $\alpha_i,\dots,\alpha_n$. This will come as an
application of the effective Nullstellensatz given in~\cite{EN}, for
which we first need to determine degree bounds, separately in $\Xb,T$
and $\A,$ of the polynomials in the membership relationship. We have
\begin{align*}
\deg_{\Xb,T}\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\}&\leq d,\\
\deg_{\A}  
\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\}& \leq d,\\
\deg_{\Xb,T}(1-T\pjb) &\leq (2d)^n +1,\\
\deg_{\A}(1-T\pjb)& \leq (2d)^n.
\end{align*}
For each $j \in \{i,\hdots,n\},$ a direct application of \cite[Theorem
0.5]{EN}, gives $\deg(\alpha_j) \le (n+1)d^n((2d)^n+1)$; we will use
the slightly less precise bound $\deg(\alpha_j) \le 2n(2d)^{2n}$.

We saw in Section~\ref{ssec:Hi1} that $\D_{i,1}$ has degree at most
$2nd^{2n}$, and all $D_j$'s have degree at most $(2d)^n$. This gives
the upper bound
$$\deg(\D_i) \le 2nd^{2n} + 2n^2(2d)^{2n} + n(2d)^n \le 6n^2 (2d)^{2n}.$$
This completes the proof of Theorem~\ref{theo:gen}.
